%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{ulem}
\usepackage{contour}

\input{glyphtounicode}

\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}

\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\schoolSubheading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #5} \\
      \textit{\small#4} \\
      \textit{\small #6}
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{
  % \begin{minipage}{15cm}\vspace{3pt}
  \begin{itemize}
}
\newcommand{\resumeItemListEnd}{
  \end{itemize}\vspace{-4pt}
  % \end{minipage}
}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

% \begin{center}
    \textbf{\huge \scshape Ege Erdoğan} 
    \small \href{mailto:ege@erdogan.dev}{\myuline{ege@erdogan.dev}} $|$ 
    \href{https://erdogan.dev}{\myuline{Homepage}} $|$
    \href{https://linkedin.com/in/ege-erdogan}{\myuline{LinkedIn}} $|$
    \href{https://github.com/ege-erdogan}{\myuline{GitHub}} $|$
    \href{https://scholar.google.com/citations?user=HjcFsdcAAAAJ&hl=en&oi=ao}{\myuline{Google Scholar}}
    \vspace{8pt}
% \end{center}

\small{Updated \today. See \href{https://erdogan.dev/resume}{\myuline{erdogan.dev/resume}} for latest version.} \vspace{-7pt}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \schoolSubheading
      {Koç University (GPA: 3.57/4)}{Istanbul, Turkey}
      {Double major in Computer Engineering \& Mathematics}
      {Cryptography, Security, and Theory specialization program $(3.91/4)$}{2017 -- Present}
      {Dean's Honor Roll (3 semesters) and Vehbi Koc Scholar (2 semesters) for academic achievement.}
    \resumeSubheading
      {Üsküdar American Academy}{Istanbul, Turkey}
      {High School}{2012 -- 2017}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
    {Research Intern}{July 2020 -- Present}
    {Koç University Cryptography, Security, and Privacy Research Group}{Istanbul, Turkey}
  \resumeItemListStart
    \resumeItem{\textbf{Supervisor:} Assoc. Prof. Alptekin Küpçü}
    \resumeItem{Working on the design and implementation of novel offensive and defensive methods involving \\ privacy-preserving machine learning systems.}
    \resumeItem{Produced two first-author papers (see Research section below), currently under review; one is \\ a set of attacks targeting data and model confidentiality of split learning clients, the other is a method by which \\ split learning clients can detect and prevent \textit{training-hijacking} attacks.}
    \resumeItem{Using Python and various ML libraries to implement privacy-preserving machine learning \\ methods and attacks against them. }
  \resumeItemListEnd

  \resumeSubheading
    {Undergraduate Tutor}{Feb. 2021 -- June 2021}
    {Koç University}{Istanbul, Turkey}
  \resumeItemListStart
    \resumeItem{Held weekly tutoring sessions and helped with course administration\\ for the \textit{Computer Networks} course for the Spring 2021 semester.}
  \resumeItemListEnd

  \resumeSubheading
    {Undergraduate Teaching Assistant}{Sep. 2020 -- Jan. 2021}
    {Koç University}{Istanbul, Turkey}
  \resumeItemListStart
    \resumeItem{Conducted weekly problem solving sessions and held office hours for the \textit{Introduction \\ to Programming with Python} course during the Fall 2020 semester.}
  \resumeItemListEnd

  \resumeSubheading
    {Software Development Intern}{July 2020 -- Aug. 2020}
    {Proteams}{Istanbul, Turkey}
  \resumeItemListStart
    \resumeItem{Implemented features for different parts of a mobile application, including its \\ back-end server, database, and admin panel.}
    \resumeItem{Worked with Java and the Spring framework for the backend, PostgreSQL for the database, \\ and Angular for the admin panel.}
  \resumeItemListEnd

  \resumeSubheading
    {Summer Intern}{July 2019}
    {IBM}{Istanbul, Turkey}
  \resumeItemListStart
    \resumeItem{Worked within the IBM Cloud \& Cognitive team.}
    \resumeItem{Built a chatbot to answer questions by IBM new hires as a group with the other interns.}
    \resumeItem{Developed a music generation system using neural networks and built a web interface for it \\ with the other interns. Worked with Python for machine learning and web development.}
  \resumeItemListEnd

  \resumeSubheading
    {Software Development Intern}{Feb. 2018 -- April 2018}
    {Bitlo Cryptocurrency Exchange}{Istanbul, Turkey}
  \resumeItemListStart
    \resumeItem{Started learning and gained experience using the Spring framework to build web \\ applications. Gained practice with the Java language.}
  \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PUBLICATIONS-----------
\section{Research}
\begin{enumerate}
    \item \textbf{Ege Erdogan}, Alptekin Kupcu, A. Ercument Cicek. “SplitGuard: Detecting and Mitigating Training-Hijacking Attacks in Split Learning”, 2021; \href{https://arxiv.org/abs/2108.09052}{\myuline{arXiv:2108.09052}}. \textit{[Preprint. Under review.]}

    \item \textbf{Ege Erdogan}, Alptekin Kupcu, A. Ercument Cicek. “UnSplit: Data-Oblivious Model Inversion, Model Stealing, and Label Inference Attacks Against Split Learning”, 2021; \href{https://arxiv.org/abs/2108.09033}{\myuline{arXiv:2108.09033}}. \textit{[Preprint. Under review.]}
    
    \item \textbf{Ege Erdogan}, Can Arda Aydin, Oznur Ozkasap, Waris Gill. “Demo -- Zelig: Customizable Blockchain Simulator”, 2021; \href{https://arxiv.org/abs/2107.07972}{\myuline{arXiv:2107.07972}}. \textit{[Accepted for presentation at the 40th International Symposium on Reliable Distributed Systems (SRDS 2021)]}
\end{enumerate}


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Zelig: Customizable Blockchain Simulator} (work-in-progress) $|$ \emph{Python}}{}
          \resumeItemListStart
            \resumeItem{Building a blockchain simulator in Python with the core goals of customizability and extensibility, aiming to address the shortcomings of existing simulators.}
            \resumeItem{Started as a term project for the Distributed Systems course and resumed as independent work.}
            \resumeItem{Accepted to be presented at the demo session of the 40th International Symposium on Reliable Distributed Systems (SRDS 2021).}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Brick-breaking Game} $|$ \emph{Java, Swing, MongoDB}}{}
          \resumeItemListStart
            \resumeItem{Developed a brick-breaking game as a group of 5 for the Software Engineering course at Koc University.}
            \resumeItem{Worked with Java Swing libraries for the visuals, and used MongoDB to save user statistics and save games.}
            \resumeItem{Gained experience with software development tools and methodologies such as agile development, UML diagrams, and design patterns.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Web-based News Reader} $|$ \emph{Ruby, Ruby on Rails, JavaScript}}{}
          \resumeItemListStart
            \resumeItem{Developed a web-based reader scraping and displaying content from Hacker News, Slashdot, and the r/programming subreddit as a solo project.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Course Projects}}{}
          \resumeItemListStart
            \resumeItem{Various course projects including Distributed Systems, AI/ML, Computer Security, Computer Networks, Operating Systems, and Digital Design courses among others can be found at \href{https://github.com/ege-erdogan/coursework}{\myuline{https://github.com/ege-erdogan/coursework}}.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd


% ------------- ACTIVITIES --------------
\section{Activities}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Volunteer} $|$ \emph{Koc University Entrepreneurship Society}}{2019-2020}
          \resumeItemListStart
            \resumeItem{Volunteered as a mentor for the \textit{Zero to One} entrpreneurship conference.}
            \resumeItem{Worked in the organization of the conference and was responsible of a group of guests on event day.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Member} $|$ \emph{Uskudar American Academy Percussion Group}}{2013-2017}
          \resumeItemListStart
            \resumeItem{Was a member of the UAA percussion group.}
            \resumeItem{Participated in various concerts with the group in Belgium, Ankara, Izmir, and Istanbul.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Skills \& Interests}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Human Languages}{: Turkish (native), English (fluent), German (beginner)  \\
     \textbf{Computer Languages}{: Python, Java, JavaScript, Go, Ruby, C, Scheme} \\
     \textbf{Frameworks/Libraries} \\
     \ \ \ \ \textbf{Machine learning/Statistics}{: PyTorch, Numpy, Matplotlib, scikit-learn} \\
     \ \ \ \ \textbf{Web}{: Ruby on Rails, Spring, Bootstrap} \\
     \textbf{Areas of interest}{: Security \& privacy, machine learning, cryptography, web development, theoretical CS} \\ 
    %  \textbf{Hobbies}{: Cycling, playing basketball, cooking (not necessarily at the same time)}
    }}}
 \end{itemize}


%-------------------------------------------
\end{document}
